FIXME

### 2013-09-10 writeups/proposal/proposal.tex
Tue commits
Former-commit-id: 87d03def9e1f62687c64ecd435baafba1e4b3011 [formerly e7d234e46c49fcbd0d1e3744b699a90f67e4d322]
Former-commit-id: 13370119671ebe0ddde061fe58504b386456aa28

\usepackage{graphicx}
\usepackage[group-separator={,}]{siunitx}
\RequirePackage[l2tabu, orthodox]{nag}
\graphicspath{{./figures/}} % Specifies the directory where pictures are stored

@@

Two models will be evaluated for hashtag prediction on both the Twitter and StackOverflow datasets:
A vector-based model and Bayesian retrieval model.
The random permutation model \parencite{Sahlgren2008} in Table \ref{tabRandPermModel} will be used for the vector-based model, since it has shown to perform better than the BEAGLE model \parencite{Recchia2010}.
The modified ACT-R Bayesian model \parencite{Stanley2013} in Table \ref{tabModACTRMOdel} will be used for the Bayesian model, since it has already been applied to tag use on StackOverflow posts.

@@

@@

\cite{DataDump2013}

@@

TODO: common-hashtags dataset
TODO: popular-users dataset

\subsection{Tokenizing and Lemmetizing Text}

TODO: Python NLP toolkit \cite{Bird2009}

@@

>>>>

\usepackage{subfigure}
\usepackage{graphicx}
\usepackage[group-separator={,}]{siunitx}
\RequirePackage[l2tabu, orthodox]{nag}
\graphicspath{{./figures/dissertation/}} % Specifies the directory where pictures are stored

@@

Two models will be evaluated for hashtag prediction on both the Twitter and StackOverflow datasets:
A vector-based model and Bayesian retrieval model.
The random permutation model \parencite{Sahlgren2008} in Table \ref{tabRandPermModel} will be used for the vector-based model, since it has shown to perform better than the BEAGLE model \parencite{Recchia2010}.
The modified ACT-R Bayesian model \parencite{Stanley2013} in Table \ref{tabModACTRModel} will be used for the Bayesian model, since it has already been applied to tag use on StackOverflow posts.

@@

A modified ACT-R declarative memory retrieval model and random-permutation vector-based model will be evaluated on predicting user-chosen tags for Twitter tweets and StackOverflow posts.
Parameters for each model will be calibrated on a large subset of the Twitter and StackOverflow datasets.
Each model will be tested by evaluting the accuracy of model-chosen-tags on a fresh test subset of the datasets.
Accuracy will be assessed by comparing model performance with the human data.

@@

% FIXME: Verify these numbers
The most recent quarterly-published StackOverflow dataset \parencite{DataDump2013} will be used to test the models on user-chosen tags for posts.
This dataset contains around 5 million posts and \num{30000} unique tags.
The site requires that for each post, the user must associate at least one tag with the post.
The post author is allowed to choose multiple tags for the post.
The average number of tags per post is around 3.

% FIXME: Use a different example figure
\begin{figure}[ht]
  \resizebox{\linewidth}{!}{\includegraphics{visPost-2977094-screen-crop.pdf}}
  \caption{Example post on stackoverflow.com}
  \label{figSOExample}
\end{figure}

An example StackOverflow post is included in Figure \ref{figSOExample}.
The author used 4 tags for this post: \emph{javascript}, \emph{firefox}, \emph{dom}, and \emph{svg}.

@@

% FIXME: Verify these numbers
Unlike StackOverflow, the entire Twitter dataset is not released to the public.
Due to this and the sheer size of all of Twitter, subsets of the Twitter dataset must be collected.
So two Twitter datasets will be collected for model evaluation:
A common-hashtags and popular-users dataset.
The common-hashtags dataset contains approximately 2 million tweets containing at least one of the 20 most popular hashtags.
This dataset was collected over a period of 2 days.
The purpose of this dataset is to test the accuracy of each model's predicted most likely hashtag(s) for a tweet.

The popular-users dataset will contain all of the tweets from the top \num{2000} users on Twitter.
This dataset will be used to explore the growth and decay characteristics of a hashtag for a single user.
The temporal dynamics of ACT-R's decay rate model for a chunk will be evaluated against this data.
As a result, the most appropriate model of user-centered frequency and recency effects (i.e., each hashtag's prior likelihood given a particular user) will be determined.

% FIXME: Use actual tweet figures
\begin{figure}[ht]
  \hfill
  \subfigure[Title A]{\includegraphics[width=8cm]{tweet-screen-crop.pdf}}
  \hfill
  \subfigure[Title B]{\includegraphics[width=8cm]{tweet-screen-crop.pdf}}
  \hfill
  \caption{Example tweets on Twitter.com}
  \label{figTweetExample}
\end{figure}

% FIXME: Write summary paragraph for twitter tweets figures.

\subsection{Pre-processing the Text}

The text from all dataset will be pre-processed using standard natural-language processing techniques.
The Python NLP toolkit \parencite{Bird2009} will be used to tokenize (chunk) and lemmetize (convert to root form) each word.
The standard chunking algorithm will be modified, so that it also ensures that hashtags and tag words (e.g., the word \emph{PHP} in a post) are not separated into multiple chunks.
With the StackOverflow dataset, it is possible to convert synonym tags to canonical base tags, since the community maintains a tag-synonym database.
So tag words in the post and used tags for the post will be converted to their root tag when applicable.

@@

\subsection{Attentuating Spam Posts}

\cite{Mazzia2009}
